% -----------------------------------------------------------------------------
% Master thesis in the study program computational mechanics
%
% B.Sc. Rezha Adrian Tanuharja - 03751261
% M.Sc. Felix Schneider (supervisor)
%
% chapters/methodology/caseStudy.tex
% Last edited 03 November 2023
% -----------------------------------------------------------------------------

\section{Case Study}
\label{sec: case study}

This study demonstrates the practical application of the new framework using a simple yet relevant example: a plate clamped at both of its ends.
The choice of case is deliberate, as it is sufficiently large for the substructuring methods while still maintaining the feasibility of direct MC simulations.
Figure \ref{fig: case study} illustrates the plate and its dimensions.

\input{images/caseStudy}

Table \ref{table: Plate Parameter} lists the relevant plate's parameters.
The plate's density and thickness are uncertain and modeled by random variables.
The parameters $\xi_{1}$ and $\xi_{2}$ are statistically independent standard normal random variables.

\begin{table}[H]
    \setlength{\extrarowheight}{2pt}
    \centering
    \begin{tabular}{
        L{0.32\textwidth}rccC{0.25\textwidth}
    }
        \hline
        Parameter & \multicolumn{3}{c}{Value} & Unit \\
        \hline
        Thickness &
            $(1.0+0.2\xi_{1})$ & $\times$ & $0.01$ &
            \einheit{m} \\
        Density & 
            $(1.0+0.2\xi_{2})$ & $\times$ & $7850.0$ &
            \einheit{kg/{m}^{3}} \\
        Shear modulus & 
            \multicolumn{3}{c}{$79.3$} &
            \einheit{GPa} \\
        Shear correction factor & 
            \multicolumn{3}{c}{$0.83$} &
            -- \\
        Poisson ratio & 
            \multicolumn{3}{c}{$0.3$} &
            -- \\
        \hline
    \end{tabular}
    \caption{Plate's Parameters in The Case Study}
    \label{table: Plate Parameter}
\end{table}

Two discrete models approximate the plate using the FE method with Kirchoff plate theory: the complete plate model and the substructured plate model.
The proposed framework uses the latter to generate training data for the NI-RPCE models, which will approximate the complete plate model.
On the other hand, the FRFs from direct MCS using the complete plate model serve as the baselines for comparison.

\input{chapters/methodology/caseStudy/completeModel}
\input{chapters/methodology/caseStudy/substructuredModel}
\input{chapters/methodology/caseStudy/surrogateModel}